Iterative Monomorphisation

### 2024-05-17 iterative_monomorphisation.tex
filled out table 6

@@

\begin{table}[ht]
\caption{Evaluation of native polymorphism vs.\ monomorphisation}
\centering\begin{tabular}{@{}lccc@{}}
   \toprule
   & Native & Mono & Union \\
   \midrule
   E  &   & 0 & 0 \\
   Leo-III & 0 & 0 & 0 \\
   Satallax &  & 0 & 0 \\
   Vampire & 0 & 0 & 0 \\
   Zipperposition & 0 & 0 & 0 \\[1.5\jot]
   Total & 0 & 0 & 0 \\
   \bottomrule
\end{tabular}
\end{table}

\begin{table}[ht]
\caption{Evaluation of Zipperposition without E vs. with E}
\centering\begin{tabular}{@{}lccc@{}}
   \toprule
   & without E & with E & Union \\
   \midrule
   Zipperposition & 0 & 0 & 0 \\
   \bottomrule
\end{tabular}
\end{table}

>>>>

We conducted two evaluations of Zipperpostion with the monomorphisation algorithm and E as a backend. The first was on the 500 problems we used for option optimisatio and the second on the remaining 1034 problems. This version of Zipperposition was compared against the base Zipperposition prover. The base Zipperposition instance was run wiht the sequential portfolio mode \verb|portfolio.sequential.py|.

Note that Zipperposition's portfolio mode seems to consider timeouts to be more of a polite suggestion than a hard limit, we consequently added a manual timeout of 30 seconds.

\begin{table}[ht]
\caption{Evaluation of Zipperposition without E vs. with E}
\centering\begin{tabular}{@{}lccc@{}}
   \toprule
   & without E & with E & Union \\
   \midrule
   500 problems benchmark   & 152 & 185 & 195 (-10 +43) \\
   fresh problems benchmark & 337 & 385 & 419 (-34 +82)\\
   \bottomrule
\end{tabular}
\end{table}

@@

\begin{table}[ht]
\caption{Evaluation of native polymorphism vs.\ monomorphisation}
\centering\begin{tabular}{@{}lccc@{}}
   \toprule
   & Native & Mono & Union \\
   \midrule
   E  &   & 0 & 0 \\
   Leo-III & 0 & 0 & 0 \\ % Leo-III's performance is comparatively very poor, not coherent with casc results
   Satallax &  & 0 & 0 \\
   Vampire & 0 & 0 & 0 \\ % Vampire's parser fails on too many polymorphic problems (about 1/3 of them)
   Zipperposition & 335 & 0 & 0 \\[1.5\jot]
   Total & 0 & 0 & 0 \\
   \bottomrule
\end{tabular}
\end{table}
